---
title: "Results_Outline_Jeff"
author: "Stephanie Bland"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: word_document #html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE,echo=FALSE,fig.pos = 'H',cache.lazy = FALSE)
```
```{r hidden, include=FALSE}
#---- Hidden ----
#library(ggbiplot)
library(tidyverse)
library(stringr)
library(knitr)
z=0
```
```{r load_data}
DATE="2017Nov28"
Version="0"
location="/GIT/Analysis"#For Running on my Mac
#location=""#For Clusters
run_name=paste0(DATE,"_",Version)
setwd(paste0("~/",location,"/",run_name))
#---- LOAD_DATA ----
dat=read.table("clean.txt",header=F)
colnames(dat)=as.matrix(read.table("colnames_clean.txt"))
# The first step should be setting up better names, so the legends will automatically be named properly. This is to avoid having vague graphs with names like "experiment 1" and experiment 2" because people will definitely forget what that means.
exper_name=c("Original Web","Extended Web","Leslie & History")
# Make Processing faster, I think? - DONT USE THIS YET - IT WILL BREAK THINGS!
# dat=dat %>% mutate_at(c("isfish","basal_ls"),as.logical) %>%
#	mutate_at(c("Phase_df","Nodes_df","Seed","Exper","pred","prey","species","lifestage"),as.factor)
```
```{r DefineMultiplot}
# From https://stackoverflow.com/a/24387436
# Multiple plot function
#
# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
# - cols:   Number of columns in layout
# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
#
# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
# then plot 1 will go in the upper left, 2 will go in the upper right, and
# 3 will go all the way across the bottom.
#
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  require(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
```

## Part A: Model Realism - [Show that new models are realistic (Show our setup is good)]
```{r Percent_Stable, include=FALSE}
# Subset the data that fit criteria 1 and 2
subdat_ls=dat %>% filter(Year_df==max(Year_df),isfish==1) %>% 
	group_by(simnum,Exper) %>%
	summarise(Tot_species=sum(Biomass)) %>% # But now it needs to survive in ALL experiments
	summarise(any=sum(Tot_species),all=prod(Tot_species)) %>%
	mutate_at(c("any","all"),as.logical)
persist=subdat_ls %>% summarise_at(c("any","all"),mean)*100
# Criteria 1: Probability of fish persisting in at least one of the experiments
# Criteria 2: Probability of fish persisting in all of the experiments
subdat1=dat %>% filter(simnum %in% (subdat_ls %>% filter(any==TRUE))$simnum)
subdat2=dat %>% filter(simnum %in% (subdat_ls %>% filter(all==TRUE))$simnum)
```
Figures:

+ Fig 1a: Von Bert curves
```{r Von-Bert-Multi, fig.cap=cap}
# Caution: The clunky formatting here is because we need to plot ALL life stages if a single life stage survives. This way you won't end up with a partial line between two life stages
subdat1 %>% filter(simnum<20,Exper==3,Year_df==max(Year_df),isfish==1) %>%
	group_by(simnum,species) %>%
	mutate(tot_fish_biom=sum(Biomass)) %>% # Make sure you only grab surviving species, but make sure you grab ALL nodes
	filter(tot_fish_biom>0) %>% # Can't filter by Biomass>0 because some life stages go extinct and you end up with incomplete curves
	ungroup() %>%
	mutate(species=factor(as.integer(species)+(39*simnum)),lifestage=as.integer(lifestage),simnum=as.factor(simnum)) %>% 
	#select(simnum,species,Biomass, tot_fish_biom,Mass)
	ggplot(aes(x=lifestage, y=log10(Mass))) + geom_line(aes(group=species, colour=simnum)) + labs(x="Fish life stage",y="log of individual body mass")

z=z+1;VBmult=z
cap=paste("Figure",VBmult,"Von-Bertalanffy curves for surviving fish in several simulated food webs. Each colour represents a different food web.")
```

```{r Von-Bert-Multi2, fig.cap=cap}
VB_orig_fish=subdat1 %>% filter(simnum<20,Exper==3,Year_df==max(Year_df),isfish==1) %>%
	group_by(simnum,species) %>%
	mutate(tot_fish_biom=sum(Biomass)) %>% # Make sure you only grab surviving species, but make sure you grab ALL nodes
	ungroup() %>%
	mutate(species=factor(as.integer(species)+(39*simnum)),lifestage=as.integer(lifestage),simnum=as.factor(simnum)) %>% 
	#select(simnum,species,Biomass, tot_fish_biom,Mass)
	ggplot(aes(x=lifestage, y=log10(Mass))) + geom_line(aes(group=species, colour=simnum)) + labs(x="Fish life stage",y="log of individual body mass")

# Caution: The clunky formatting here is because we need to plot ALL life stages if a single life stage survives. This way you won't end up with a partial line between two life stages
VB_end_fish=subdat1 %>% filter(simnum<20,Year_df==max(Year_df),isfish==1) %>%
	group_by(Exper,simnum,species) %>%
	mutate(tot_fish_biom=sum(Biomass)) %>% # Make sure you only grab surviving species, but make sure you grab ALL nodes
	filter(tot_fish_biom>0) %>% # Can't filter by Biomass>0 because some life stages go extinct and you end up with incomplete curves
	ungroup() %>%
	mutate(species=factor(as.integer(species)+(39*simnum)),lifestage=as.integer(lifestage),simnum=as.factor(simnum)) %>% 
	group_by(Exper) %>%
	do(g=ggplot(.,aes(x=lifestage, y=log10(Mass))) + geom_line(aes(group=species, colour=simnum))  + labs(x="Fish life stage",y="log of individual body mass"))

#multiplot(VB_orig_fish, VB_end_fish$g[[1]], VB_end_fish$g[[2]], VB_end_fish$g[[3]],cols=1)

#z=z+1;VBmult2=z
#cap=paste("Figure",VBmult2,"Von-Bertalanffy curves for surviving fish in several simulated food webs. Each colour represents a different food web.")
```

+ Fig 1b: Allometric Ratios are invariant
```{r VB-Hist}
VB_orig=dat %>% filter(Year_df==1,Exper==1) %>%
	group_by(simnum) %>%
	mutate(scaled_mass=10^5*Mass/max(Mass)) %>%
	filter(lifestage==4)
VB_hist_orig = VB_orig %>% ggplot(.,aes(Z))+geom_histogram() + coord_cartesian(xlim=c(min(VB_orig$Z),max(VB_orig$Z))) + labs(x="Allometric Ratio")

VB_hist=subdat1 %>% filter(Year_df==max(Year_df),Biomass>0) %>%
	group_by(Exper,simnum) %>%
	mutate(scaled_mass=10^5*Mass/max(Mass)) %>%
	filter(lifestage==4)
```

```{r VB_Exper_compare, fig.cap=cap,echo=FALSE}
meh=VB_hist %>% group_by(Exper) %>%
	do(k=ggplot(.,aes(Z))+geom_histogram()+coord_cartesian(xlim=c(min(VB_orig$Z),max(VB_orig$Z))) + labs(x="Allometric Ratio"))
multiplot(VB_orig_fish, VB_end_fish$g[[1]], VB_end_fish$g[[2]], VB_end_fish$g[[3]],
		  VB_hist_orig, meh$k[[1]], meh$k[[2]], meh$k[[3]], cols=2)

z=z+1;VB_Exper_compare=z
cap=paste("Figure",VB_Exper_compare,"A histogram of the allometric ratios for all the surviving adult fish life stages.")
```

```{r Mass_Overlap}
mass_overlap=dat %>% filter(Year_df==1,Exper==1,isfish==1,lifestage %in% range(lifestage)) %>%
	select(simnum,species,lifestage,Mass) %>%
	group_by(simnum) %>%
	spread(key=lifestage,value=Mass) %>%
	summarise(youngest_large=max(`1`),oldest_small=min(`4`)) %>%
	mutate(range_overlap=youngest_large<oldest_small,size_ratio=oldest_small/youngest_large)
percent_range_overlap=mass_overlap %>% summarise(100*sum(range_overlap)/n())
hist(log10(mass_overlap$size_ratio),main="",xlab="Allometric ratio of the oldest small fish to the youngest large fish (log10)")

z=z+1;mass_overlap_cap=z
cap=paste("Supplementary Figure",mass_overlap_cap,"A histogram of the logged allometric ratios between the oldest life stage of the smallest fish species and the youngest life stage of the largest fish species for any model.")
```

# Logic for text:

Our model produces realistic life histories for fish species.
Since we are using an allometric trophic network model, mass is unitless and all that matters is the relative ratios of predator to prey within the same model.
You can not compare mass across simulations.
We already know that adult fish have realistic weight ranges because our model produces adults with the same lognormal distribution for body mass as Tonin's model.
Fish extinctions are equally probable across the lognormal distribution of allometric ratios, so fish species are not disproportionately skewed by size range in any of our models (fig `r VB_Exper_compare`b). 

The growth curves for new life stages are also realistic.
Individual fish species have realistic growth curves as they are defined to follow the von-Bertalanffy function defined in the methods. 
Fish also have realistic body size ranges for their growth, as there is a large overlap between the size ranges for species within each web (fig `r VB_Exper_compare`a).
Webs have an overlap between all the fish species size ranges `r percent_range_overlap`% percent of the time.

# Text (Alternate version, says the same thing as above):

Our model produces realistic von-Bertalanffy growth curves (fig `r VB_Exper_compare`a). Since we are using an allometric trophic network model, mass is unitless and all that matters is the relative ratios of predator to prey within the same model. You can not compare mass across simulations. However, fish species within simulations tend to be in the same size range, as the weight range for fish species often overlap each other. The youngest life stage of the largest fish species is smaller than the oldest life stage of the youngest fish `r percent_range_overlap`% percent of the time. The growth curves for any given species are also realistic, as we defined the curve to follow a von-Bertalanffy growth function. Our model produces fish species with realistic allometric ratios (fig `r VB_Exper_compare`b), and fish extinctions are equally probably across the lognormal distribution of allometric ratios, so our model is not favouring fish of any particular body mass. 

## Part B: General simulation Output (Start looking at time series results, and compare model types
Figures:
Fig 2: Time Series for a linked Model
```{r TS_solo, fig.cap=cap}
subdat2 %>% filter(Exper==3,simnum==unique(simnum)[4]) %>%
	mutate(lifestage=as.factor(lifestage),species=as.factor(isfish*species)) %>%
	group_by(Year_df,lifestage,species) %>%
	mutate(Biomass=sum(Biomass)) %>% ungroup() %>% mutate(species=c("Other","Fish 1","Fish 2","Fish 3")[species]) %>%
	ggplot(aes(x=Year_df,y=log10(Biomass))) + geom_line(aes(group=Nodes_df, colour=species,linetype=lifestage)) + labs(x="Year",y="Biomass (log 10)")

z=z+1;TSsolo=z
cap=paste("Figure",TSsolo,"A typical time series for experiment 1. This shows the logged biomass at the end of each year cycle for each fish life stage along with the combined biomass of the rest of the ecosystem.")
```

Fig 3: Hist of number of surviving species (a=0,1,2,3; b=none,all)
```{r freq_extant_fish, fig.cap=cap}
xkcd=dat %>% filter(Year_df==max(Year_df),isfish==1) %>%
	group_by(Exper,simnum,species) %>% 
	summarise(extant=as.logical(sum(Biomass))) %>%
	summarise(Num_extant=sum(extant)) %>%
	ungroup() %>% mutate(Exper=as.factor(Exper)) %>%
	group_by(Num_extant,Exper) %>%
	summarise(n=n()) %>% group_by(Exper) %>%
	mutate(Freq=n/sum(n))

xkcd1=xkcd %>% 
	ggplot(., aes(x=Num_extant, y=Freq)) + geom_point(aes(group=Exper, color=Exper))+ labs(x="Number of surviving fish species", y="Frequency of simulations")
xkcd2=xkcd %>% filter(Num_extant %in% range(Num_extant)) %>%
	mutate(Num_extant=as.factor(Num_extant)) %>%
	ggplot(., aes(x=Num_extant, y=Freq)) + geom_point(aes(group=Exper, color=Exper))+ labs(x="Number of surviving fish species", y="Frequency of simulations")+ scale_x_discrete(labels=c("None","All"))
multiplot(xkcd1,xkcd2)

z=z+1;freq_ex_fish=z
cap=paste("Figure",freq_ex_fish,"The frequency of fish surviving in each experiment.")
```

Fig 4a: CV of tot biomass against Model type
```{r CV_total, fig.cap=cap}
# Coefficient of Variation Function
CV <- function(dat){sd(dat)/mean(dat)*100}
sem <- function(x) {sd(x,na.rm=T)/sqrt(sum(is.na(x)))} # Standard error

CV_plot=subdat2 %>% group_by(Exper,simnum,Year_df) %>%
	filter(Phase_df==2) %>%
	summarise(Tot_bio=sum(Biomass),Tot_fish=sum(isfish*Biomass)) %>%
	summarise(CV_tot=CV(Tot_bio),CV_fish=CV(Tot_fish)) # %>% ### So here we see the CVs for fish and total
	#summarise_at(c("CV_tot","CV_fish"),c(mean,sem))

boxplot(CV_tot~Exper,CV_plot,xlab="Experiment",ylab="Coefficient of Variation")

#ggplot(CV_plot,aes(x=Exper,y=CV_tot))+geom_boxplot() + xlab("Experiment") + ylab("Mean Coefficient of Variation") + labs(caption="Figure 3 Box plots for the CV of the total biomass.")

z=z+1;totCV=z
cap=paste("Figure",totCV,"The coefficient of variation for the total biomass in each experiment")
```

Fig 4b: CV of fish biomass against Model type
```{r CV_fish, fig.cap=cap, include=F}
boxplot(CV_fish~Exper,CV_plot,xlab="Experiment",ylab="Coefficient of Variation") 
#	labs(caption="Figure 4 The CV of total fish biomass.")

z=z+1;fishCV=z
cap=paste("Figure",fishCV,"The coefficient of variation for the total fish biomass in each experiment")
```

- (Maybe, if time permits) - A comparison plot of time series for diff sims and models in supplementary

Text:
`r persist$any`% of our simulations met the criteria for the first part of the analysis, meaning fish stabilized in at least one of the experiments. `r persist$all`% of our simulations met the second criteria, where at least one fish must stabilize in every experiment. It was anticipated that some simulations would never stablize, given that we placed minimal constraints on food webs during the web creation stage. Thus, some of the webs would invariably end up being completely biologically unrealistic. This process of weeding out unstable webs might seem unintuitive at first, but it mimics what we observe in nature. Just as natural landscapes are eventually populated by stable ecosystems after a long process of species invasions and extinctions. A typical time series of the simulation for a food web that eventually stabilizes is illustrated in figure `r TSsolo`.

## Part C: Output for linked model
Figures:

+ Fig 5: Life History correlation plots

Text:










